---
title: "R Notebook"
output: html_notebook
---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
#for small margin = <=10%
df <- data.frame('Counties w/ Big Cities' = c(54, 13), "Counties w/o Big Cities" = c(721,143))
row.names(df) <- (c('Counties with Margins >10%', 'Counties with Margins <=10%'))
df
chisq.test(df) #chi-square test of significance
fisher.test(df) #fisher's exact test of significance
```

H0, the null hypothesis in this case, is "There is no relationship between whether a county contains a city and whether the margin is large or small."
H1, the alternative hypothesis, is "There IS a relationship between whether a contains a city and the margin."

We should not reject the null hypothesis because the p-value is very large (suggesting that this could easily have happened randomly).
This is pretty interesting and potentially refutes the argument of whether cities are actually more liberal, at least in swing states.

```{r}
#for small margin = <=2%
df <- data.frame('Counties w/ Big Cities' = c(63, 4), "Counties w/o Big Cities" = c(834,30))
row.names(df) <- (c('Counties with Margins >2%', 'Counties with Margins <=2%'))
df
chisq.test(df) #chi-square test of significance
fisher.test(df) #fisher's exact test of significance
```
H0, the null hypothesis in this case, is "There is no relationship between whether a county contains a city and whether the margin is large or small."
H1, the alternative hypothesis, is "There IS a relationship between whether a contains a city and the margin."

Interesting, same results, even for 1%, maybe because the n is really small. Fisher gets closer to significance, but if we want our threshhold to be 0.05, which I definitely should, we still cannot reject the null hypothesis. 

We should not reject the null hypothesis because the p-value is very large (suggesting that this could easily have happened randomly).

```{r}
#Alternative Hypothesis: Counties with cities are more likely to have Margins > 0 than counties without cities 
df <- data.frame('Counties w/ Big Cities' = c(54, 13), "Counties w/o Big Cities" = c(220,644))
row.names(df) <- (c('Counties with Positive Marginal Votes', 'Counties with Negative Marginal Votes'))
df
chisq.test(df) #chi-square test of significance
fisher.test(df) #fisher's exact test of significance
```
